When are Fuzzy Extractors Possible?

### 2015-01-06 trunk/info-bounds/FuzzyExtPossibility.tex
adding reviewer comments

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.  We compare our positive results to these characterizations in \secref{sec:known distributions}.

@@

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution over $(\mathcal{M}, \dis)$ and let $n= \log |\mathcal{M}|$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
 with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

@@

\paragraph{Generalizing to correlated random variables}
Instead of considering $w, w'$ that have bounded distance, we can treat $W, W'$ as a pair of correlated random variables.  
  Renner and Wolf~\cite{DBLP:conf/asiacrypt/RennerW05} study this setting, firsting consider information-reconciliation and privacy amplification separately.  They show that $\Hoo(W)$ is a necessary and sufficient condition for privacy amplification.\footnote{The results of Renner and Wolf use smooth notions of entropy.  A random variable has smooth entropy if it is statistically close to a distribution with true entropy. We describe their results in the terminology of non smooth entropy.}  Second, they show that the length of $p$ must grow with the worst case number of possible outcomes for $W$ conditioned on $W'$.\footnote{This result also uses a smooth notion of entropy.  We describe the non smooth version for simplicity.}  That is, the length of the public value \[|p|\ge \max_{w'\in W} \log |\{w | \Pr[W=w | W'=w']>0\}|.\]

Lastly, the work of Renner and Wolf shows characterize when key derivation is possible from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.  We compare this characterization to fuzzy min-entropy in \secref{sec:known distributions}.

Fuzzy min-entropy can be generalized to this setting.   Fuzzy extractors consider the worst case $w'$.  When considering correlated readings, it is natural to treat $W'$ as a random variable:\footnote{Fuzzy extractors are defined to require high probability of correctness for all pairs $w, w'$.  In the correlated setting, it may make sense to provide an average-case guarantee, where the probability of correctness is also over the draw of $w, w'$.  Renner and Wolf use a smoothed notion of entropy that removes the $\delta$ fraction of the probability mass of $W=w|W'=w'$ with the most points to improve parameters under such a definition.  In this work, we consider worst case correctness and use unsmoothed entropy.}

\begin{definition}
\label{def:cor fuzz min}
Let $(W, W')$ be a pair of correlated random variables.  The correlated fuzzy min-entropy of $W, W'$ is:
\[\Hcorr(W, W') = -\log \left( \max_{w'\in \supp(W')}\sum_{w\in W | \Pr[W=w|W'=w']>0} \Pr[W = w] \right).\]
\end{definition}
\noindent 
In \defref{def:fuzzy min-ent}, the sum is implicitly over $W=w|W'=w'$ since we assume any $w'$ within distance $t$ is possible.  
For now, we consider sufficiency of $\Hfuzz(W)$ for key derivation from noisy sources (\defref{def:fuzzy min-ent}). We then consider the implications of our results on the correlated reading setting (\defref{def:cor fuzz min}).

@@

@@

%\begin{corollary}
%\label{cor:no fuzz for dist}
%Let $\mathcal{W}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
%\end{corollary}
%
%Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
\section{Proof of \propref{prop:fuzz necessary}}
\label{sec:proof fuzz necessary}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(w', p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
Clearly, $\Pr[D(\Key, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
Note that $D$ only provides an input and looks at the output, thus it extends to an interactive protocol.  Also, $D$ is of size $\max |\mathcal{M}|+ |\rep|$ where $\max |\mathcal{M}|$ is the longest description of an item in the metric space.  Thus, $D$ is also a distinguisher in the computational setting.
\end{proof}

@@

The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.  The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  There are $n$ outcomes for $i$. The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le m+n}2^{-(i+1)}\beta_{t,i}&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
&= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
-\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on 
\[
2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | 2^{-(n+m)}<\Pr[W=w]}\Pr[W=w | \sketch(W)].
\]
We separate out this quantity into levels:
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-(m+n)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{|\sketch(W)|i|}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*\beta_{t,i}/\delta\right)\\
&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}

@@

\begin{lemma}
\label{lem:secure sketch entropy loss}
Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  Dealing with imperfect correctness makes the bound more complicated.  In particular, we can only argue about the average remaining support size.}
\end{lemma}
\begin{proof}
We assume that $\rec$ is deterministic in our analysis.  Any randomness necessary for the \rec algorithm can be provided by \sketch.  This is the same as considering $\rep$ that outputs any coin it flips.  Since $w, w'$ are independent of $p$ this does not effect correctness.  Security is defined based on the output of $\rec$ so outputting the coins of $\rep$ does not effect security.
By the definition of correctness for $(\sketch, \rec)$, 
\[
\forall w, w', \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) \neq w] < 1/4.
\]
%For most $p$, $\rec$ works on most neighbors of $w$.  
Fix some $w$.  
By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[ss\in A_{ss}]\ge 1/2$ and $\forall ss\in A_{ss}$, 
\[
\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]

Consider some $ss^*\in A_{ss}$.  We now show that $H_0(V | \sketch(V) = ss^*) \le (\gamma-t+1)\log |\mathbb{F}|$.  For the sketched value $w$, $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.

For every value in $V|\sketch(V) = ss^*$ this is also true.  This makes the support of $V|\sketch(V)=ss^*$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).  This implies that for all $w_1, w_2 \in V|\sketch(V)=ss^*$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).  That is $V|\sketch(V)=ss^*$ is a set with minimum distance at least $t$.

By the Singleton bound, this implies that $H_0(V |\sketch(V)=ss^*) \le (\gamma -t+1 )|\mathbb{F}|$.  Averaging over $\sketch(V)=ss^*$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
\end{proof}

\begin{lemma}
\label{lem:side info determines sketch}
$\Hav(V | \sketch(V), Z) <2$.
\end{lemma}
\begin{proof}
Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
 As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.  %Having seen $V$ there are many possible values for $Z$.  Furthermore, the distributions $V|Z$ have disjoint support outside of the observed point.  
 The only information seen by $\sketch$ algorithm is in the point $V=v$.  The length of this point is $|\mathbb{F}|^\gamma$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
 \[
 \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}}{|\mathbb{F}|^\gamma}\right) = \log \left( (|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|\right).
 \]
Consider two possible $z_1, z_2$ that are possible values of $Z$~(having seen $v$).  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).

>>>>

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.  We compare our positive results to these characterizations in \apref{sec:corr variables}.  To the best of our knowledge, prior results on correlated random variables are in the known distribution setting, we are unaware of works that consider security for families of distributions.

@@

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
\bnote{Should note this is the ideal security of a noisy source, both in the interactive/non-interactive settings}
Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution over $(\mathcal{M}, \dis)$ and let $n= \log |\mathcal{M}|$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
 with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

@@

\bnote{I feel we can provide a more general results than this one.  Helpful?}

@@

\section{Key Derivation from Correlated Random Variables}
\label{sec:corr variables}

In this work, we consider two draws from some physical source whose distance was bounded according to some metric space.
Instead of considering $w, w'$ that have bounded distance, we can treat $W, W'$ as a pair of correlated random variables.  
  Renner and Wolf~\cite{DBLP:conf/asiacrypt/RennerW05} study this setting, firsting consider information-reconciliation and privacy amplification separately.  They show that $\Hoo(W)$ is a necessary and sufficient condition for privacy amplification.\footnote{The results of Renner and Wolf use smooth notions of entropy.  A random variable has smooth entropy if it is statistically close to a distribution with true entropy. We describe their results in the terminology of non smooth entropy.}  Second, they show that the length of $p$ must grow with the worst case number of possible outcomes for $W$ conditioned on $W'$.\footnote{This result also uses a smooth notion of entropy.  We describe the non smooth version for simplicity.}  That is, the length of the public value \[|p|\ge \max_{w'\in W} \log |\{w | \Pr[W=w | W'=w']>0\}|.\]

Lastly, the work of Renner and Wolf shows characterize when key derivation is possible from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.  Fuzzy min-entropy can be generalized to this setting.   Fuzzy extractors consider the worst case $w'$.  When considering correlated readings, it is natural to treat $W'$ as a random variable:\footnote{Fuzzy extractors are defined to require high probability of correctness for all pairs $w, w'$.  In the correlated setting, it may make sense to provide an average-case guarantee, where the probability of correctness is also over the draw of $w, w'$.  Renner and Wolf use a smoothed notion of entropy that removes the $\delta$ fraction of the probability mass of $W=w|W'=w'$ with the most points to improve parameters under such a definition.  In this work, we consider worst case correctness and use unsmoothed entropy.}

\begin{definition}
\label{def:cor fuzz min}
Let $(W, W')$ be a pair of correlated random variables.  The correlated fuzzy min-entropy of $W, W'$ is:
\[\Hcorr(W, W') = -\log \left( \max_{w'\in \supp(W')}\sum_{w\in W | \Pr[W=w|W'=w']>0} \Pr[W = w] \right).\]
\end{definition}
\noindent 
In \defref{def:fuzzy min-ent}, the sum is implicitly over $W=w|W'=w'$ since we assume any $w'$ within distance $t$ is possible.  
In \secref{sec:known distributions} we showed sufficiency  of $\Hfuzz(W)$ for key derivation from noisy sources (\defref{def:fuzzy min-ent}).

@@

%\begin{corollary}
%\label{cor:no fuzz for dist}
%Let $\mathcal{W}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
%\end{corollary}
%
%Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
\section{Proof of \propref{prop:fuzz necessary}}
\label{sec:proof fuzz necessary}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(w', p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
Clearly, $\Pr[D(\Key, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
Note that $D$ only provides an input and looks at the output, thus it extends to an interactive protocol.  Also, $D$ is of size $\max |\mathcal{M}|+ |\rep|$ where $\max |\mathcal{M}|$ is the longest description of an item in the metric space.  Thus, $D$ is also a distinguisher in the computational setting.
\bnote{this should probably be in the body of the paper}
\end{proof}

@@

The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.  The adversary chooses 
\[
w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w')}\Pr[W=w].
\] 
The success of this adversary is at least $2^{-(i+1)}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  There are $n$ outcomes for $i$. The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le m+n}2^{-(i+1)}\beta_{t,i}&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
&= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
\bnote{need to clean up this proof}
We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on 
\[
2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | 2^{-(n+m)}<\Pr[W=w]}\Pr[W=w | \sketch(W)].
\]
We separate out this quantity into levels:\bnote{we need to talk about K here}\bnote{we were asked what $\Pr[W=w| \sketch(W)]$ means, to me that's well formed}\bnote{shouldn't there be a term here $\Pr[L_i = i]$?}
\begin{align*}
\max_{w\in W | 2^{-(m+n)}< \Pr[W=w]}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\frac{2^{-i}*\beta_{t,i}}{\delta}\right)\\
&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) &\ge -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}

@@

\begin{lemma}
\label{lem:secure sketch entropy loss}
Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  Dealing with imperfect correctness makes the bound more complicated.  In particular, we can only argue about the average remaining support size.}
\end{lemma}
\begin{proof}
We assume that $\rec$ is deterministic in our analysis.  Any randomness necessary for the \rec algorithm can be provided by \sketch.  This is the same as considering $\rec$ that outputs any coin it flips.  Since $w, w'$ are independent of $ss$ this does not effect correctness.  Security is defined based on the output of $\rec$ so outputting the coins of $\rec$ does not effect security.
By the definition of correctness for $(\sketch, \rec)$, 
\[
\forall w, w', \dis(w, w') \le t, \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) \neq w] < 1/4.
\]
%For most $p$, $\rec$ works on most neighbors of $w$.  
Fix some $w$.  
By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[ss\in A_{ss}]\ge 1/2$ and $\forall ss\in A_{ss}$, 
\[
\frac{|\{w' | \dis (w', w)\le t \wedge \rec(w', ss) \neq w\}|}{|\{w'|\dis(w', w) \le t\}|}\le 2\delta < 1/2.\]

Consider some $ss^*\in A_{ss}$.  We now show that $H_0(V | \sketch(V) = ss^*) \le (\gamma-t+1)\log |\mathbb{F}|$.  For the sketched value $w$, at most a $2\delta$ fraction of nearby $w'$ do not map to $w$. Thus, this is also true for every value in $V|\sketch(V) = ss^*$ this is also true.    This makes the support of $V|\sketch(V)=ss^*$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).  This implies that for all $w_1, w_2 \in V|\sketch(V)=ss^*$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).  That is $V|\sketch(V)=ss^*$ is a set with minimum distance at least $t$.

By the Singleton bound, this implies that $H_0(V |\sketch(V)=ss^*) \le (\gamma -t+1 )|\mathbb{F}|$.  Averaging over $\sketch(V)=ss^*$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
\end{proof}
\bnote{the reviewer is complaining that $V | \sketch(V)$ is not a distribution.  don't know why}
\begin{lemma}
\label{lem:side info determines sketch}
$\Hav(V | \sketch(V), Z) <2$.
\end{lemma}
\begin{proof}
Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
 As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.  %Having seen $V$ there are many possible values for $Z$.  Furthermore, the distributions $V|Z$ have disjoint support outside of the observed point.  
 The only information seen by $\sketch$ algorithm is in the point $V=v$.  The length of this point is $|\mathbb{F}|^\gamma$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
 \[
 \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}}{|\mathbb{F}|^\gamma}\right) = \log \left( (|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|\right).
 \]
Consider two possible $z_1, z_2$ that are possible values of $Z$~(having seen $v$).  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).
